### 2016-08-26 analysis-note-v2/Appendix.tex
update the fits for the free proton asymmetries and update all the ALU ratio plots

\chapter{Free proton beam-spin asymmetry interpolation} 
\label{app:free-proton-alu}
\section{Fitting the experimentally measured asymmetries}
Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
coherent and the incoherent beam-spin asymmetries to free proton asymmetries 
reveal new information about the nuclear medium modifications. To construct 
such ration, the published free proton asymmetries \cite{FX_BSA} have been used 
in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ in the 
different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
asymmetries were calculated at the same incoherent and coherent measured 
kinematics. The statistical errors on the calculated asymmetries were 
calculated using the error bars on the fitted parameters $t_{min}$, $p_0$, and 
$p_1$.\\

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.85]{fig_updated/ALU-proton-fits.pdf}
\caption{Black circles are the free proton beam-spin asymmetries at $\phi = 90 
^{circ}$ as a function of $-t$ in different ($x_B, Q^2$) bins as measured at 
CLAS-E1DVCS experiment. The solid red curves are fits to the free proton 
asymmetries in the form $p_{0}*(t-t_{min})*e^{p_{1}*\sqrt{t}}$. The dashed 
curves are calculations using the fitted $t_{min}$, $p_0$, and $p_1$ parameters 
as a function of $x_B$ as shown in figure \ref{fig:fitted-points-xB}. Blue 
points are the interpolated points corresponding for the incoherent points 
presented in this analysis. Red points are extrapolated free proton points at 
the coherent kinematical values.}
\label{fig:free-proton-alu}
\end{figure}

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.37]{fig_updated/tmin-xB-fit.png}\\
\includegraphics[scale=0.37]{fig_updated/p0-xB-fit.png}\\
\includegraphics[scale=0.37]{fig_updated/p1-xB-fit.png}
\caption{The fitted $t_{min}$, $p_0$, and $p_1$ parameters as a function of 
$x_B$.}
\label{fig:free-proton-alu}
\end{figure}

\section{Model-dependent extraction}
The proton asymmetries have been adjusted using a dispersion calculation 
including a phenomenological GPD $H$ only. The imaginary part of the amplitude 
is parameterized as in \cite{GPD_cal_free_p}. The real part of the amplitude is 
then obtained from the dispersion relation and the D-term as subtraction 
constant, parameterized as in \cite{GPD_cal_free_p}. The beam spin asymmetries 
mostly constrain the parameters of the imaginary part, and the unpolarized 
cross-section mostly constrain the D-term parameters.

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.55]{fig_updated/From_FX_Check_Fit_6GeV_asym.png}
\caption{The free proton beam-spin asymmetries at $\phi = 90^{circ}$ as a 
function of $-t$ in different ($x_B, Q^2$) bins as measured at CLAS-E1DVCS 
experiment. The solid red lines are the model calculations based on the 
kinematics of each bin. The blue points stand for the interpolated free proton 
asymmetries at the kinematics of our incoherent and coherent DVCS channels.}
\label{fig:free-proton-alu}
\end{figure}

>>>>

\chapter{Free proton beam-spin asymmetry interpolation} 
\label{app:free-proton-alu}
\section{Fitting the experimentally measured asymmetries} \label{fit_int} 
Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
coherent and the incoherent beam-spin asymmetries to free proton asymmetries 
reveal new information about the nuclear medium modifications. To construct 
such ratio, the published free proton asymmetries \cite{FX_BSA} have been used 
in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ for 
the different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
asymmetries were calculated at the same measured incoherent and coherent
kinematic values.  The statistical errors on the calculated asymmetries were 
calculated using the error bars on the fitted parameters $a_{i}$s.\\

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.85]{fig_updated/ALU-proton-fits.pdf}
\caption{Black circles are the free proton beam-spin asymmetries at $\phi = 90 
   ^{\circ}$ as a function of $-t$ in different ($x_B, Q^2$) bins as measured 
   at CLAS-E1DVCS experiment. The solid red curves are fits to the free proton 
   asymmetries in the form $a_{0}*(\sqrt{t}-a_{1})*e^{a_{2}*\sqrt{t} - a_{3}}$.  
   The dashed curves are calculations using the fitted $a_{i}$'s parameters as 
a function of $x_B$ as shown in figure \ref{fig:fitted-points-xB}. Blue points 
are the interpolated points corresponding for the incoherent points presented 
in this analysis. The red points stand for the extrapolated free proton 
asymmetries at the measured coherent kinematics.}
\label{fig:free-proton-alu}
\end{figure}

\begin{figure}[tpb]
\includegraphics[scale=0.37]{fig_updated/test_a0.pdf}
\includegraphics[scale=0.37]{fig_updated/test_a1.pdf}
\includegraphics[scale=0.37]{fig_updated/test_a2.pdf}
\hspace{1.7cm}
\includegraphics[scale=0.37]{fig_updated/test_a3.pdf}
\caption{The fitted $a_0$, $a_1$, $a_2$, and $a_3$ parameters as a function of 
$x_B$.}
\label{fig:fitted-points-xB}
\end{figure}

\section{Model-dependent extraction} \label{model_int}
The proton asymmetries have been adjusted using a dispersion calculation 
including a phenomenological GPD $H$ only. The imaginary part of the amplitude 
is parameterized as in \cite{GPD_cal_free_p}. The real part of the amplitude is 
then obtained from the dispersion relation and the D-term as subtraction 
constant, parameterized as in \cite{GPD_cal_free_p}. The beam spin asymmetries 
mostly constrain the parameters of the imaginary part, and the unpolarized 
cross-section mostly constrain the D-term parameters. Figure 
\ref{fig:FXfree-proton-alu} presents the published free proton asymmetries with 
the model calculations, in solid red lines, and the interpolated free proton 
asymmetries at our measured coherent and incoherent kinematic values.

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.55]{fig_updated/From_FX_Check_Fit_6GeV_asym.png}
\caption{The free proton beam-spin asymmetries at $\phi = 90^{circ}$ as a 
function of $-t$ in different ($x_B, Q^2$) bins as measured at CLAS-E1DVCS 
experiment. The solid red lines are the model calculations based on the 
kinematics of each bin. The blue points stand for the interpolated free proton 
asymmetries at the kinematics of our incoherent DVCS channels.}
\label{fig:FXfree-proton-alu}
\end{figure}

\section{Summary}
In this analysis we use the interpolated values from fitting the experimentally 
measured free proton asymmetries to construct the beam-spin asymmetry ratios, 
presnted in section \ref{fit_int}.  The differences between the beam-spin 
asymmetry ratios calculated using the free proton asymmetries fits, section 
\ref{fit_int}, and the model-dependent interpolated values, section 
\ref{model_int}, were added as a systematic errors on the constructed beam-spin 
asymmetry ratios.  Table \ref{table:ALU_ratios_} presents the coherent and the 
incoherent $A_{LU}$ ratios extracted using both methods and the associated 
systematic uncertainties.

\small
\begin{landscape}
\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l|l|l||}
         \hline
 ($Q^{2}$, $x_{B}$, $-t$) & EG6 $A_{LU}$ $\pm$ stat. &  Exp. fit $\pm$ stat. & Exp. $A_{LU}$ ratio   &  Model extr. & Model $A_{LU}$ ratio &  Diff. (Exp - Model)    \\
  \hline
(1.395, 0.166, 0.407) &  0.136 $\pm$ 0.027   &    0.1691 $\pm$ 0.0592   &  0.8042 $\pm$ 0.3248  &  0.2050 &  0.6634 &  0.1408 \\
(1.886, 0.233, 0.499) &  0.156 $\pm$ 0.033   &    0.2081 $\pm$ 0.0738   &  0.7494 $\pm$ 0.3101  &  0.2244 &  0.6951 &  0.0543 \\ 
(2.338, 0.290, 0.521) &  0.154 $\pm$ 0.038   &    0.2129 $\pm$ 0.0777   &  0.7268 $\pm$ 0.3206  &  0.2177 &  0.7110 &  0.0158 \\
(3.098, 0.379, 0.650) &  0.122 $\pm$ 0.042   &    0.1765 $\pm$ 0.0676   &  0.6956 $\pm$ 0.3581  &  0.2017 &  0.6088 &  0.0868 \\
  \hline \hline  \hline                                                                                                
(1.425, 0.162, 0.397) &  0.118 $\pm$ 0.026   &    0.1686 $\pm$ 0.0587   &  0.7045 $\pm$ 0.2913  &  0.1885 &  0.6302 &  0.0743 \\
(1.922, 0.227, 0.418) &  0.178 $\pm$ 0.029   &    0.2122 $\pm$ 0.0740   &  0.8429 $\pm$ 0.3257  &  0.2135 &  0.8379 &  0.005  \\
(2.354, 0.287, 0.492) &  0.151 $\pm$ 0.036   &    0.2209 $\pm$ 0.0795   &  0.6847 $\pm$ 0.2974  &  0.2170 &  0.6972 &  0.0125 \\
(2.987, 0.390, 0.714) &  0.132 $\pm$ 0.050   &    0.1562 $\pm$ 0.0615   &  0.8457 $\pm$ 0.4661  &  0.2103 &  0.6281 &  0.2176 \\
  \hline  \hline  \hline                                                                                               
(1.823, 0.213, 0.145) &  0.146 $\pm$ 0.027   &    0.2304 $\pm$ 0.0677   &  0.6363 $\pm$ 0.2223  &  0.2438 &  0.6013 &  0.035  \\
(2.127, 0.255, 0.282) &  0.150 $\pm$ 0.031   &    0.2641 $\pm$ 0.0848   &  0.5700 $\pm$ 0.2177  &  0.2410 &  0.6248 &  0.0548 \\
(2.308, 0.284, 0.490) &  0.163 $\pm$ 0.039   &    0.2200 $\pm$ 0.0791   &  0.7400 $\pm$ 0.3209  &  0.2195 &  0.7425 &  0.0025 \\
(2.406, 0.308, 1.107) &  0.115 $\pm$ 0.054   &    0.0939 $\pm$ 0.0429   &  1.2240 $\pm$ 0.8030  &  0.1235 &  0.9311 &  0.2929 \\
  \hline  \hline  \hline                                                                                               
(1.143, 0.132, 0.096) &  0.332 $\pm$ 0.051   &    0.1821 $\pm$ 0.0528   &  1.8267 $\pm$ 0.6017  &  0.2447 &  1.3596 &  0.4671 \\
(1.423, 0.170, 0.099) &  0.353 $\pm$ 0.051   &    0.1857 $\pm$ 0.0534   &  1.9044 $\pm$ 0.6146  &  0.2518 &  1.4050 &  0.4994 \\
(1.902, 0.224, 0.107) &  0.258 $\pm$ 0.050   &    0.1835 $\pm$ 0.0524   &  1.4063 $\pm$ 0.4863  &  0.2359 &  1.0941 &  0.3122 \\
    \hline \hline  \hline                                                                                              
(1.164, 0.132, 0.095) &  0.373 $\pm$ 0.073   &    0.1819 $\pm$ 0.0529   &  2.0503 $\pm$ 0.7190  &  0.2234 &  1.6696 &  0.3807 \\
(1.439, 0.170, 0.099) &  0.267 $\pm$ 0.086   &    0.1859 $\pm$ 0.0535   &  1.4361 $\pm$ 0.6231  &  0.2432 &  1.0978 &  0.3383 \\
(1.844, 0.225, 0.107) &  0.362 $\pm$ 0.092   &    0.1830 $\pm$ 0.0522   &  1.9812 $\pm$ 0.7571  &  0.2515 &  1.4421 &  0.5391 \\
     \hline  \hline  \hline                                                                                            
(1.493, 0.177, 0.1)   &  0.326 $\pm$ 0.030   &    0.1863 $\pm$ 0.0535   &  1.7498 $\pm$ 0.5292  &  0.2453 &  1.3289 &  0.4209 \\

 \hline
 \end{tabular}
 \caption{$A_{LU}$ ratios. The first three blocks stand for the incoherent bins 
 in $Q^{2}$, $x_{B}$, and $-t$, respectively. The last three blocks are for the 
 coherent bins in $Q^{2}$, $x_{B}$, and $-t$, respectively. The first column 
 contains the mean value of the kinematical variables for each bin. The second 
 column contains EG6 measured $A_{LU}$ with the statistical error bars. The 
 third column ("Exp. fit $\pm$ stat.") contains the interpolated free proton 
 $A_{LU}$ at EG6 kinematical values from fitting the free proton beam-spin 
 asymmetries. The forth column ("Exp. $A_{LU}$ ratio") stands for the 
 calculated $A_{LU}$ ratios using EG6 asymmetries and the fitted free proton 
 asymmetries. The fifth column ("Model extr.") stands for the model-depended 
 extracted free proton asymmetries. The sixth column ("Model $A_{LU}$ ratio") 
 presents the calculated $A_{LU}$ ratios using EG6 asymmetries and the 
 model-dependent extracted free proton asymmetries. The last column ("Diff.  
 (Exp - Model)") shows the difference between the two calculated $A_{LU}$ 
 ratios for each bin.}
 \label{table:ALU_ratios_}
 \end{center}
\end{table}
\end{landscape}
